Creating Venn diagrams

### 2020-05-22 Scripts_for_results/08_creating_venn_diagrams.Rmd
added nested venn diagram section

>>>>

### Nesting between pt(arrowhead) and pt(peakachu)

res <- makeVennDiagram(Peaks=list(all_pred_bounds_gm12878_a,
                                  all_pred_bounds_gm12878_p),
                       NameOfPeaks=c("preciseTAD", "PEAKACHU"))

venn.pt <- venn_cnt2venn(res$vennCounts)
venn.pt <- compute.Venn(venn.pt)
gp <- VennThemes(venn.pt)
gp[["Face"]][["11"]]$fill <-  "purple"
gp[["Face"]][["01"]]$fill <-  "red"
gp[["Face"]][["10"]]$fill <-  "lightblue"
gp[["FaceText"]][["10"]]$cex <- 2
gp[["FaceText"]][["11"]]$cex <- 2
gp[["FaceText"]][["01"]]$cex <- 2
gp[["SetText"]][["Set1"]]$cex <- 2
gp[["SetText"]][["Set2"]]$cex <- 2

res <- makeVennDiagram(Peaks=list(all_pred_bounds_k562_a,
                                  all_pred_bounds_k562_p),
                       NameOfPeaks=c("preciseTAD", "PEAKACHU"))

venn.pt <- venn_cnt2venn(res$vennCounts)
venn.pt <- compute.Venn(venn.pt)
gp <- VennThemes(venn.pt)
gp[["Face"]][["11"]]$fill <-  "purple"
gp[["Face"]][["01"]]$fill <-  "red"
gp[["Face"]][["10"]]$fill <-  "lightblue"
gp[["FaceText"]][["10"]]$cex <- 2
gp[["FaceText"]][["11"]]$cex <- 2
gp[["FaceText"]][["01"]]$cex <- 2
gp[["SetText"]][["Set1"]]$cex <- 2
gp[["SetText"]][["Set2"]]$cex <- 2
